Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-05 tex/results.tex
Add sentence to explain y values limitation
small rewrite
fix passage mentioned by Rockstul in email

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
But, since the quantity of interest is the wavelength at which the resonance modes occur, the results can be compared.

@@

The constraints of mesh generation mean that we have only loose control on triangle density. Our meshes for the rectangular prism all have densities like in the coarse case of the grid-independence study of sub-section \ref{sec:independence}, or finer.
For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm.

>>>>

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
For example, Wiley et al.\ show simulatinon results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.

@@

The constraints of mesh generation mean that we have only loose control on triangle density. Our meshes for the rectangular prism all have densities like in the coarse case of the grid-independence study of sub-section \ref{sec:independence}, or finer.
For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We did not explore larger values of $y$ because of the limitations imposed by the quasistatic limit model.
